Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2023-01-20 code/data-wrangling.qmd
completed ATACH2, working on ERICH

>>>>

# variables needed from each dataset-----
# demographics: age, gender, site of enrollment
# pmh: hypertension, diabetes, stroke, ICH, CAD, CKD
# meds: anticoagulation, antiplatelet, lipids, bp
# presentation features: symptom onset, SBP/DBP,GCS, NIHSS
# presentation features: intubated
# imaging: ICH volume, location, IVH, midline shift?
# processes: EVD, neurosurgery, trach, PEG, WLST
# outcomes: mRS, euroQOL
